\documentclass[11pt]{article}
\usepackage{fullpage,times}

\newcommand{\squish}{
      \setlength{\topsep}{0pt}
      \setlength{\itemsep}{0ex}
      \vspace{-1.5ex}
      \setlength{\parskip}{0pt}}

\begin{document}

\begin{center} \bf{ \Large{Ari Juels}}\\ 
\vspace{2mm}
Cornell Tech\\
Jacobs Technion-Cornell Innovation Institute\\
111 8th Avenue Ave \#302, New York, NY 10011, U.S.A.\\
juels@cornell.edu\\
www.arijuels.com
\end{center}


\noindent\hrulefill
\\

\noindent 
{\Large {\bf Professional preparation}}

\vspace{-1mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
Amherst College \> B.A., Mathematics and Latin Literature \> 1991 
\end{tabbing}
\vspace{-8mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
University of California, Berkeley \> Ph.D., Computer Science \> 1996
\end{tabbing}

\bigskip

\noindent 
{\Large {\bf Appointments}}

\vspace{-1mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
Professor \> Cornell Tech \> 2014 -- Present 
\end{tabbing}
\vspace{-5mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
{Chief Scientist} \> RSA, The Security Division of EMC\> 2010 -- 2013
\end{tabbing}
\vspace{-8mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
{Distinguished Engineer} \> EMC Corporation \> 2010 -- 2013
\end{tabbing}
\vspace{-8mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
{Director} \> RSA Laboratories \> 2007 --  2013 
\end{tabbing}
\vspace{-8mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
Chief Scientist \> RSA Laboratories \> 2007 --  2010  
\end{tabbing}
\vspace{-8mm}
\begin{tabbing}
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa \= aaaaaaaaaaaaa \= \kill
Research Scientist \> RSA Laboratories \> 1996 -- 2007 
\end{tabbing}



\bigskip

\noindent
{\Large {\bf Publications}}
\\

\noindent (i) Five publications most closely related to the project:
\vspace{-2mm}
\begin{itemize}
\item A. Juels and T. Ristenpart. Honey Encryption: Security Beyond the Brute-Force Bound. EUROCRYPT, pp. 293--310, 2014.
\item A. Juels and T. Ristenpart. Honey Encryption: Encryption Beyond the Brute-Force Barrier. IEEE Security \& Privacy Magazine, 12(4): 59--62, 2014.
\item  A. Juels. A bodyguard of lies: the use of honey objects in information security. SACMAT, pp. 1-4, 2014.
\item A. Juels and R. L. Rivest. Honeywords: Making Password-Cracking Detectable. ACM Conference on Computer and Communication Security (ACM CCS), pp. 145--160, 2013.
\item A. Juels and M. Sudan. A Fuzzy Vault Scheme. Designs, Codes, and Cryptography 38(2): 237-257, 2006.
\end{itemize}

\pagebreak

\noindent (ii) Five other significant publications:
\vspace{-1mm}
\begin{itemize}
\item K. Bowers, A. Juels, and A. Oprea. {HAIL}: A High-Availability and Integrity Layer for Cloud Storage. ACM Conference on Computer and Communication Security (ACM CCS), pp. 187--198, 2009. 
\item A. Juels and B. Kaliski. PORs: Proofs of Retrievability for Large Files. ACM Conference on Computer and Communications Security (ACM CCS), pp. 584--597, 2007.
\item A. Juels.  RFID security and privacy: a research survey. Journal of Selected Areas in Communication (J-SAC) 24(2): 381--394, 2006.
\item A. Juels, R. L. Rivest, and M. Szydlo. The Blocker Tag: Selective Blocking of RFID Tags for Consumer Privacy (full version). ACM Conference on Computer and Communications Security (ACM CCS), pp. 103--111, 2003
\item A. Juels and M. Wattenberg. A Fuzzy Commitment Scheme. ACM Conference on Computer and Communications Security (ACM CCS), pp. 28--36, 1999. 
\end{itemize}

\bigskip
\vspace{-1mm}

\noindent
{\Large {\bf Recent synergistic activities}}

\begin{itemize}
\item Developed course: ``Security and Privacy Concepts in the Wild,'' CS 5435, Cornell Tech, Fall 2014
\item Co-organizer, DIMACS Workshop on Secure Cloud Computing, 2014;  Program co-chair, ACM Cloud Computing Security Workshop, 2013 
\item Postdoctoral advisor for Hussam Abu-Libdeh (Ph.D., Cornell Univ.); Recent Ph.D. committee member for: Davide Zanetti, ETH Zurich, Dec. 2012; Masoud Rostami, Rice Univ., May 2014; Yinqian Zhang, UNC, June 2014; Mathias Humbert, EPFL, December 2014 (expected); Joel Reardon, ETH Zurich, Jan. 2015 (expected)
\item Keynote and invited lectures: ACM SACMAT, keynote, June 2014; ETH Zurich, distinguished colloqium, Mar. 2014; Google / UMD Seminar Series, invited lecture; Feb., 2013; SecureCloud, invited lecture, May 2012; Schloss Dagstuhl joint seminar on cloud security, keynote, December 2011
\item Academic Advisory Board member, MIT Consortium for Kerberos and Internet Trust, 2013-; Cryptology Advisory Board, Skyhigh Networks, 2014-
\item Technical program committee participation: IEEE S\&P, 2015; NDSS, 2015; IEEE S\&P, 2014; ACM CCS, 2013; CRYPTO, 2012; NDSS, 2012; ACM CCS, 2010; EUROCRYPT, 2010
\end{itemize}

\vspace{1mm}
\noindent
{\Large {\bf Collaborators}}
\vspace{2mm}

\noindent
{\bf Graduate Advisor:} Alistair Sinclair, UC Berkeley

\bigskip
\noindent
{\bf Recent collaborators (co-authors in past four years and co-editors in past two years)}: Kevin D. Bowers (RSA Labs),
Wayne Burleson (UMass-Amherst),
Srdjan Capkun (ETH-Zurich),
Marten van Dijk (UConn),
Catherine Hart (Bell Canada),
Jonathan Katz (UMD),
Engin Kirda (NEU),
Farinaz Koushanfar (Rice Univ.),
Todd Leetham (EMC),
Andrew Miller (UMD),
Kaan Onarlioglu (NEU),
Alina Oprea (RSA Labs)
Christof Paar (R.-U. Bochum),
Bryan Parno (MSR),
Michael Reiter (UNC),
Thomas Ristenpart (UW-Madison),
Ronald L. Rivest (MIT),
William K. Robertson (NEU),
Masoud Rostami (Rice Univ.),
Emily Shen (Lincoln Labs),
Elaine Shi (UMD),
Emil Stefanov (UC Berkeley),
Nikos Triandopoulos (BU and RSA Labs),
Venkatanathan Varadarajan (UW-Madison),
Ting-Fang Yen (E8 Security),
Bonnie Wong (Harvard Medical School),
Davide Zanetti (Medtronic)
Yinqian Zhang (UNC)


\end{document}
