\section{Implementation-considerate Formalisms}
\label{sec:formalisms}
The modern ``provable security'' approach to cryptography loosely follows a
four-step recipe: define a precise syntax for the primitive under study, define
a formal notion of security for that primitive, realize the primitive,
and prove it meets the security notion. The first step, defining the syntax,
essentially defines the component objects that collectively make up the
primitive, e.g. ``An encryption scheme $\Pi$ is a triple of algorithms
$(\calK,\calE,\calD)$ ...''  The syntax typically describes the number and type
of the inputs and outputs of these components, too, e.g. ``The decryption
algorithm provides a mapping $\calD\colon\bits^{k}\times\bits^* \to \bits^* \cup
\{\bot\}$ ...'', as well as requirements on the behavior of these components in
any correct realization of them.

%\cpnote{This is great.}
%
The syntax for a new primitive provides an API for researchers. For
those wishing to \emph{realize} the primitive (in theory), it makes clear what
are the functionalities that must be instantiated, and what are the assertions that
must hold for any realization; for those wishing to \emph{use} the primitive, it
makes clear what calls will be available to them, and what are the expected
inputs and outputs of those calls.
%
Like a real software API, syntax is considered good if it serves the needs of
its ``customers''; in this case, if it supports clear security notions,
facilitates the writing (and verification) of proofs, and is easily built
upon.\footnote{As an aside, PI Shrimpton has found the analogy of
\emph{syntax-as-API} as a useful pedagogical tool. Computer science students
often seem far more familiar and comfortable with programming abstractions than
with mathematical ones.}

%Of course, this analogy only goes so far.  When a researcher argues for a change
%to the accepted syntax ---~a new API for a primitive~--- there is no real cost
%incurred if it is adopted.  Prior works using the old syntax do not
%suddenly``break''; in the worst case they may (eventually) be viewed as
%outdated.  If anything, the new syntax presents an opportunity for researchers
%revisit prior work and publish updated findings.

%\cpnote{I think you should add a nonce to the AEAD syntax below, as I think is
%usual. This also gives you an opportunity to discuss the issue with nonces in
%practice: that there's not always an obvious choice for a nonce, programmer's
%don't know how/why to use them, etc.}
%
Of course, there is a considerable gap between the formal syntax that papers
provide and a \emph{real} API, i.e., the functionalities that need to be
implemented. For example, the well-established syntax for symmetric-key
decryption with associated data is a deterministic algorithm $\calD\colon\calK
\times \calH \times \bits^* \to \bits^* \cup \{\bot\}$, where $\calK$ and
$\calH$ are sets, the first finite and the second possibly infinite. We
cryptographers would typically write something like $M \gets \calD^{\,H}_K(C)$
for the decryption of ciphertext~$C\in\bits^*$, with associated data~$H \in
\calH$, under key~$K \in \calK$.  But this quietly assumes a number of implicit
functionalities that must be attended to in practice.

First of all, the formal syntax assumes that~$H$ and~$C$ are simply presented as
inputs. In reality the decryption process may need to parse (aka deserialize,
unmarshall) what is received from the channel into the ciphertext~$C$ and any
context information (aka associated data) that was sent with~$C$. (For example,
the TLS ciphertext stream encodes the length of each encrypted record.)
Moreover, the overall decryption process may depend on both the context that is
associated to this ciphertext transmission \emph{and} on context that the
receiver maintains for the channel. (Note that the syntax is silent as to the
source of the associated data; it may have been transmitted with~$C$ or made
available locally.) In practice the receiver may maintain local message
counters, lists of nonces already observed on the channel,
%\cpnote{More likely it
%would just keep the largest valid nonce observed, since this requires only constant
%space.}\tsnote{Can't do that if you want to allow for nonces that are
%randomly generated, which is not uncommon.  Concretely, QUIC was
%specified to keep a strike-list of observed nonces.}  
information about the
overall status and health of the channel (e.g. is it still considered active),
and so on.  The decryption key~$K$ is also part of the context that the receiver
maintains.

Next, the formal syntax says that decryption returns a
string or a distinguished symbol~$\bot$, the latter being traditionally
understood by cryptographers to mean ``invalid''.  In practice, this means that
some logic must be implemented to decide (in)validity, and that when the
decision is ``invalid'' some error-handling mechanism ensures that the
decryption process returns nothing but a distinguished error message.

\begin{figure}[t]
  \begin{center}
    \fpage{0.58}{
      \underline{\algfont{DECRYPT}(\rwordfont{var} \varfont{ChannelContext}, \varfont{Msg}):}
      \begin{align*}
        &(\varfont{SentContext},\varfont{Ciphertext}) \gets\algfont{Deserialize}(\varfont{Msg})\\
        &(\varfont{ExternalVals, InternalVals}) \gets \algfont{Decrypt}(
            \rwordfont{var}\;\varfont{ChannelContext},\varfont{SentContext}, \varfont{Ciphertext})\\
        &\varfont{Verdict} \gets \algfont{IsValid}(\varfont{InternalVals})\\
        &\varfont{ExternalVals} \gets
                                    \algfont{ErrHandler}(\rwordfont{var}\;\varfont{ChannelContext},
                                    \varfont{Verdict}, \varfont{ExternalVals})\\
        &\varfont{Return} \varfont{ ExternalVals}
      \end{align*}
    }
  \end{center}
%
\caption{Describing symmetric-key decryption of received message~\varfont{Msg} in terms of
  explicit functionalities that must be realized. All variables are passed by
  value except those preceded by the keyword \rwordfont{var}. The
  \varfont{ChannelContext} is receiver-maintained information about the channel,
  and may contain values shared with the sender (e.g., the key, channel ID),
  along with local state.  The \varfont{SentContext} is context data associated
  to this particular ciphertext. The \varfont{ExternalVals} include the message
  and are intended to be released to the external caller, and the
  \varfont{InternalVals} are intended for use only within the decryption process
  boundary.  The types of all input and output values are implicit.}
\label{fig:syntax-api-example}
\end{figure}
%
In Figure~\ref{fig:syntax-api-example}, we give an example of a more
API-like presentation of decryption.  In fact, what this gives a
framework for specifying a wide variety of schemes.  We will specify
two schemes within this framework shortly.

Making these implied functionalities more explicit has several benefits.  The
most obvious is helping developers to see what they need to implement, rather
than assuming they will be able to correctly tease out what's needed.
Conversely, it prompts the theoretician to think in terms of abstractions that
appear in practice.
%
For both developer and theoretician, this style of presentation can surface a
clearer picture of what security demands of these functionalities. For example,
specifying error handling as an explicit functionality\footnote{Following
Rogaway and Stegers~\cite{RS09}, variables are passed by value except where
annotated by \rwordfont{var}. In this case they are passed by reference so that
their value may be modified by the caller.}
\[
\varfont{ExternalVals} \gets
                                  \algfont{ErrHandler}(\rwordfont{var}\;
                                  \varfont{ChannelContext},
                                  \varfont{Verdict}, \varfont{ExternalVals})
\]
more naturally prompts one to consider questions, like, what \varfont{ExternalVals} should
be returned for a given \varfont{Verdict}, and what
security-relevant information might be leaked by them?  How should the
\varfont{ChannelContext} be updated for a given \varfont{Verdict}?

In Figure~\ref{fig:EtM-aead} we give two potential realizations of the
functions needed for decryption. In particular, they specify the components of
Figure~\ref{fig:syntax-api-example} used to realize \algfont{DECRYPT}. 

On the left side of the figure, we give a realization of conventional
encrypt-then-MAC (EtM) AEAD, following what we theoreticians consider as best practice.  Namely, if the tag check fails, then
one should label the ciphertext as invalid, and suppress all output other than
the single error message ``Invalid''.
Additionally, when ``Invalid'' is returned, the channel status field
of \varfont{ChannelContext} is changed to ``closed''.
%
%\cpnote{This needn't be mandatory. Getting ``invalid'' from \algfont{DECRYPT}
%indicates that the channel is possibly under attack. It may make sense to keep
%the channel alive if this happens only once, and to close it if it happens a
%lot.}\tsnote{True, but my statement is correct.  This \emph{is} what
%the theory says is best practice.}

On the right side, we give a more complex (and arguably realistic) EtM-style realization that includes
in the \varfont{ChannelContext} a list of valid tokens that are used within
the decryption process. It also allows for a stream ID (sid) as part
of the transmitted AD (i.e. the \varfont{SentContext}).  In the
absence of any decryption errors, the decryption process will return
(as the output of \algfont{ErrHandler}) the stream ID and the
plaintext.  If the tag check fails, then the
\varfont{Verdict} that is returned by \algfont{IsValid} is either
``Invalid'', or $\langle\mbox{"Invalid"},\mbox{"BadToken"}\rangle$,
depending on whether or not the token ID (tid) recovered within
\algfont{Decrypt} is in the token list.  In either case, the
decryption process returns ``Invalid'' and the channel status field
of \varfont{ChannelContext} is changed to ``closed'', as on the left.
If the tag check \emph{succeeds} but the recovered tid is invalid,
then the decryption process still returns ``Invalid'', but the
\varfont{ChannelContext} is not changed.  One can imagine that this might be a real-world
  behavior, where a ciphertext-validity failure is fatal to the
  channel, but a bad token is considered less of an infraction. 
  Say, if the cost to tear down/set up a new
  channel is considered unreasonable for the given application. In the
  latter case, perhaps the application requests retransmission, or sends an
  \emph{application layer} error message back through the channel.
We note that by making the specification of the functionalities
explicit, we clearly surface at least two possible attack models.  If
the adversary sees and can access the channel only, then only the
\varfont{ExternalVals} are observed; whereas if the adversary sees
things at the boundary of the decryption process, both the
\varfont{ExternalVals} and portions of the \varfont{ChannelContext}
may be visible.


%\tsnote{Say that this may seem like overkill for ``simple'' primitives
%like symmetric-key decryption, but that (1) it only seems that way
%because we are already implicitly thinking about what it means for
%things to be valid, etc., and (2) we ``know'' not to do certain things
%because mistakes were made in the past, by people who didn't know at
%the time --- hindsight is 20-20.}

\begin{task}
{We will reconsider the traditional formalisms for cryptographic primitive from an implementation considerate perspective, and establish security notions with respect to the new syntax. }
\end{task}

%\tsnote{Need to address head-on the complaint that this is going to
%  make for more complicated analysis.}

There are, of course, other ways to handle decryption errors than described in
Figure~\ref{fig:EtM-aead}; the ``right way'' is highly dependent on the setting
in which the scheme is used. However, its API
(Figure~\ref{fig:syntax-api-example}) offers a feature that is useful in all
real-world applications: it explicitly separates the \emph{message} and
\emph{error} in the output.
%
Indeed, virtually all APIs that we are aware of separate these.  Errors have
varying degrees of severity: some are \emph{fatal}, requiring the connection be
torn down; some are simply \emph{warnings} that leave to the application the
decision to process the message or to tear down the connection; and some might
be completely benign, indicating, e.g., that more data is available for reading,
or that the end-of-file has been reached.

We are aware of no work that explicitly separates the message and error in this
manner.
%
Some works consider a richer semantics for the error~\cite{BDPS13,FPMG15}, but
even these couple the message and error so that one of these is output, but
never both.  This suggest another secure-channels task.

\begin{task}
  In our study of secure channels (Task 3) we will explore the implications of
  separating the message and error in the output of decryption.
\end{task}

\ignore{
\paragraph{Prior Work. }
%
\todo{Look at Rogaway's online-AE paper.  I seem to remember him
  saying that the main contribution of that paper was API oriented}
\cpnote{\cite[Section 5]{HRRV15}: ``We provie a new notion for online-AE ... To
accurately model the underlying goal, not only must the security definition
depart from [prior work], but so too must a scheme's basic syntax. In
particular, we adopt an API-based view, where the segmentation of a plaintext is
determined by the caller.''}
}

\include{syntax-api-example}
