% CV for Thomas Ristenpart

\documentclass[10pt]{article}

\usepackage{url}
\usepackage{setspace}
%\usepackage{multibib}
\usepackage[hmargin=.75in,top=0.5in,bottom=1in]{geometry}

%\newcites{pub,man}{,Masters Thesis}

\newcommand{\hpagess}[4]{
        \begin{tabular}{cc}
        \begin{minipage}[c]{#1\textwidth} #3 \end{minipage} & 
        \begin{minipage}[c]{#2\textwidth} #4 \end{minipage}
        \end{tabular}
    }

\newcommand{\highlight}[1]{\textsf{\emph{#1}}}
\newcommand{\schighlight}[1]{{#1}}

\newcommand{\bigline}[1]
      {\setlength{\unitlength}{.01in}
      \begin{picture}(#1,1) \put(#1,5){\line(-1,0){#1}} \end{picture}}

\newcommand{\authorfont}[1]{\textnormal{#1}}
\newcommand{\marker}{*\hspace*{.3em}}
%\newcommand{\secfont}[1]{{\textbf{\Large{#1}}}}
%\newcommand{\secfont}[1]{\bigline{30}\textbf{\Large{\hspace*{10pt}#1}}}
\newcommand{\secfont}[1]{\textbf{\Large{#1}}\medskip}

\newcommand\Tvsp{\rule{0pt}{2.6ex}}
\newcommand\Bvsp{\rule[-1.2ex]{0pt}{0pt}}
\newcommand{\TabPad}{\hspace*{5pt}}
\newcommand\TabSep{@{\hspace{5pt}}|@{\hspace{5pt}}}
\newcommand\TabSepLeft{|@{\hspace{5pt}}}
\newcommand\TabSepRight{@{\hspace{5pt}}|}
 
\newcommand{\mycite}[1]{[\ref{#1}]}
\newcommand{\mycitee}[2]{[\ref{#1},\,\ref{#2}]}
\newcommand{\myciteee}[3]{[\ref{#1},\,\ref{#2},\,\ref{#3}]}

\newcommand{\sep}{0em}
\newcommand{\secsep}{\vspace*{1.50em}}
\newcommand{\inconsep}{\vspace*{8pt}}
\newcommand{\leftper}{.16}
\newcommand{\leftperpub}{.105}
\newcommand{\contentper}{.75}
\newcommand{\contentperpub}{.75}
\newcommand{\halfcontentper}{.375}

\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup} 

\newcommand{\squishenum}{
   \begin{enumerate}
    { \setlength{\itemsep}{0pt}      \setlength{\parsep}{3pt}
      \setlength{\topsep}{3pt}       \setlength{\partopsep}{1pt}
      \setlength{\leftmargin}{-0.5em} \setlength{\labelwidth}{1em}
      \setlength{\labelsep}{0.5em} } }

\newcommand{\squishenumend}{
	\end{enumerate}	}

\newcommand{\myitemize}{
   \begin{list}{$*$}
    {  \setlength{\leftmargin}{4em} \setlength{\labelwidth}{2em}
       } }


\newcommand{\myitemizeend}{
    \end{list}  }

\newcounter{Lcount}
\newcommand{\myenum}{
\begin{list}{[\arabic{Lcount}]}
{ \usecounter{Lcount}
%\setlength{\itemsep}{0pt}
%\setlength{\parsep}{0pt}
%\setlength{\topsep}{0pt}
%\setlength{\partopsep}{0pt}
\setlength{\leftmargin}{4.3em}
\setlength{\labelwidth}{2em}
%\setlength{\labelsep}{0.5em} 
} }

\newcommand{\myenumend}{
\end{list} }


\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}      \setlength{\parsep}{5pt}
      \setlength{\topsep}{3pt}       \setlength{\partopsep}{0pt}
      \setlength{\leftmargin}{3.5mm} \setlength{\labelwidth}{1em}
      \setlength{\labelsep}{0.5em} } }


\newcommand{\squishend}{
    \end{list}  }


\newcommand{\cdotlarge}{\bullet}

%\settowidth{\cvlabelwidth}{\cvlistheadingfont Spring 2004-present}

\begin{document}
%\begin{cv}{}
%\small

\begin{center}
\textbf{\Large{Thomas Ristenpart}}\\\smallskip
\textbf{Assistant Professor}\\
\textbf{Department of Computer Sciences}\\
\textbf{University of Wisconsin -- Madison}\\
 {rist@cs.wisc.edu} \\
 {\url{www.cs.wisc.edu/~rist/}}  
\end{center}
\vspace*{-1.5em}

\noindent\hrulefill
\\

%\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}cc}
%    \multicolumn{2}{c}{\textbf{\Large{Thomas C. Ristenpart}}}\\
%    \multicolumn{2}{c}{808 F Street \#309}\\
%    \multicolumn{2}{c}{Davis, CA 95616}\\
%    \multicolumn{2}{c}{530-297-6538}\\
%    \multicolumn{2}{c}{tcristenpart[at]ucdavis.edu}\\
%    \multicolumn{2}{c}{http://wwwcsif.cs.ucdavis.edu/$\sim$ristenpa/}\\
%\end{tabular*}

%\secsep 

% EDUCATION
%\section*{Education}

%%%%%
{%\setstretch{1.2}
\noindent\secfont{Professional Preparation}

%\begin{itemize}
\begin{tabular}{lll}
  \schighlight{University of California, Davis}  & Computer Science \& Engineering & B.S. 2003\\
  \schighlight{University of California, Davis}  & Computer Science \& Engineering & M.S. 2005\\
  \schighlight{University of California, San Diego}  & Computer Science & Ph.D. 2010
\end{tabular}

%\myitemizeend 


\iffalse
\halign{\hspace{2em} #\hfil  &\hspace{2em} #\hfil  &\hspace{4.5em}\hfil  # \cr
            \marker  \emph{University of California, San Diego}
                    & Ph.D. in Computer Science \hspace*{10em}& \textsf{June 2010}\cr}\smallskip

\noindent \hspace*{3em}Advisor: Professor Mihir Bellare 

\bigskip


\halign{ \hspace*{2em} #\hfil  &\hspace{2em} #\hfil  &\hspace{4.5em}\hfil  # \cr
			\marker  \emph{University of California, Davis}\hspace*{2em}
                    & M.S. in Computer Science \hspace*{10.45em}& \emph{June 2005}\cr}\smallskip

\noindent \hspace*{3em}Advisor: Professor Matt Bishop  \hspace*{3.8em}
``Time Stamp Synchronization of Distributed Sensor Logs:\\ 
\hspace*{21.2em}
 Impossibility Results and Approximation Algorithms''

\bigskip

\halign{\hspace*{3em} #\hfil  &\hspace{2em} #\hfil  &\hspace{8.5em}\hfil  # \cr
            \marker  \emph{University of California, Davis}\hspace*{2em}
                    & B.S. in Computer Science \& Engineering & \emph{June 2003}\cr}
					\fi
}
\bigskip

\noindent\secfont{Appointments}


\myitemize
\item \highlight{Assistant Professor} \hspace*{6em} 2011  --  present\\
\hspace*{3em} Department of Computer Sciences\\
\hspace*{3em} \schighlight{University of Wisconsin -- Madison}

\item \highlight{Graduate student researcher} \hspace*{2.3em} 2005  --  2010\\
\hspace*{3em} \schighlight{UC San Diego}
%\item \highlight{Visiting researcher}, \schighlight{U.~of Lugano (Switzerland)}, 
%                    Apr~2008 -- Jun~2008
%\item \highlight{Visiting researcher}, \schighlight{U.~of Washington}, Jun~2008 -- Sep~2008
\item \highlight{Graduate student researcher} \hspace*{2.3em} 2003 -- 2005\\
\hspace*{3em} \schighlight{UC Davis}
%\item \highlight{Software security intern}, \schighlight{Center for Computing Sciences}, ~2004 -- Aug~2004
%\item \highlight{Software development engineering intern}, \schighlight{Microsoft}, Jun~2001 -- Sep~2001 \& Jun~2002 -- Sep~2002
%\item \highlight{Software engineering intern}, \schighlight{Micron Technologies, Inc.}, Jun~1999 -- Sep~1999 \& Jun~2000 -- Sep~2000
\myitemizeend




\bigskip
\noindent\secfont{Publications}
%\medskip

\renewcommand{\labelenumi}{[\arabic{enumi}]}

\noindent
(i) Related Publications
\myenum

\item \label{DCRS13}
\authorfont{K.~Dyer, S.~Coull, T.~Ristenpart, and T.~Shrimpton}.
Protocol Misidentification Made Easy with Format-Transforming Encryption.
\emph{Computer and Communications Security~-- CCS 2013}, ACM, 2013

\item \label{BRRS09}
\authorfont{M.~Bellare, T.~Ristenpart, P.~Rogaway, and T.~Stegers}.
Format-Preserving Encryption.
  \emph{Selected Areas in Cryptography~-- SAC `09}, LNCS vol. 5867, pp.
  295--312. Springer, 2009

\item \label{LDJRS14}
\authorfont{D. Luchaup, K. Dyer, S. Jha, T. Ristenpart, and T. Shrimpton}.
LibFTE: A Toolkit for Constructing Practical Format-Abiding Encryption Schemes.
\emph{USENIX Security Symposium}, USENIX, 2014

\item \label{LSRJ14}
\authorfont{D. Luchaup, T. Shrimpton, T. Ristenpart, S. Jha}.
Formatted Encryption Beyond Regular Languages.
\emph{Computer and Communications Security~-- CCS 2014}, ACM, 2014

\item \label{JR14}
\authorfont{A.~Juels and T.~Ristenpart}.
Honey Encryption: Security Beyond the Brute-force Bound.
\emph{Advances in Cryptology~-- Eurocrypt 2014}, Springer, 2014

\newcounter{Lcount_saved}
\setcounter{Lcount_saved}{\value{Lcount}}
\myenumend



\iffalse
\item \label{RTSS09}
\authorfont{T.~Ristenpart, E.~Tromer, H.~Shacham, and S.~Savage}.
Hey, You, Get Off of My Cloud: Exploring Information Leakage in
  Third-party Compute Clouds.
%In E.~Al-Shaer, S.~Jha, and A.~D. Keromytis, eds., 
\emph{Computer and Communications Security~-- CCS~`09}, pp. 199--212. ACM, 2009


  \item \label{PRS11}
\authorfont{K.~Paterson, T.~Ristenpart, and T.~Shrimpton}.
Tag Size Does Matter: Attacks and Proofs for the TLS Record Protocol.
\emph{Advances in Cryptology~-- ASIACRYPT~`11}, LNCS vol.~7073, pp.~372--389, Springer, 2011


\item \label{ZJRR12}
\authorfont{Y. Zhang, A.~Juels, M.~Reiter, and T.~Ristenpart}.
Cross-VM Side Channels and their Use to Extract Private Keys.
\emph{Computer and Communications Security~-- CCS~`12}, ACM, 2012

\item \label{VKFRS12}
\authorfont{V.~Varadarajan, T.~Kooburat, B.~Farley, T.~Ristenpart, and M.~Swift}.
Resource-Freeing Attacks: Improve Your Cloud Performance (at Your Neighbor's Expense)
\emph{Computer and Communications Security~-- CCS~`12}, ACM, 2012


\item \label{FVBJRS12}
\authorfont{B.~Farley, V.~Varadarajan, K.~Bowers, A.~Juels, T.~Ristenpart, and M.~Swift}.
More for Your Money: Exploiting Performance Heterogeneity in Public Clouds
\emph{Symposium on Cloud Computing~-- SOCC~`12}, ACM, 2012.
\fi


\bigskip


\noindent (ii) Other Publications:
\myenum
\setcounter{Lcount}{\value{Lcount_saved}}

\item \label{RTSS09}
\authorfont{T.~Ristenpart, E.~Tromer, H.~Shacham, and S.~Savage}.
Hey, You, Get Off of My Cloud: Exploring Information Leakage in
  Third-party Compute Clouds.
%In E.~Al-Shaer, S.~Jha, and A.~D. Keromytis, eds., 
\emph{Computer and Communications Security~-- CCS~`09}, pp. 199--212. ACM, 2009

\item \label{DRS09}
\authorfont{Y.~Dodis, T.~Ristenpart, and T.~Shrimpton}.
Salvaging Merkle-Damg{\aa}rd for Practical Applications.
\emph{Advances in Cryptology~-- EUROCRYPT `09}, LNCS
  vol. 5479, pp. 371--388. Springer, 2009


\item \label{ZJRR14}
\authorfont{Y. Zhang, A. Juels, M. Reiter, and T. Ristenpart}.
Cross-tenant Side-channel Attacks in PaaS Clouds
\emph{Computer and Communications Security~-- CCS 2014}, ACM, 2014


\item \label{RY10}
\authorfont{T.~Ristenpart and S.~Yilek}.
When Good Randomness Goes Bad: Virtual Machine Reset Vulnerabilities
  and Hedging Deployed Cryptography.
\emph{Network and Distributed Systems Security~-- NDSS~`10}, ISOC,
  2010


%\item \label{BBNRSSY09}
%\authorfont{M.~Bellare, Z.~Brakerski, M.~Naor, T.~Ristenpart, 
%G.~Segev, H.~Shacham, and S.~Yilek}.
%Hedged Public-key Encryption: How to Protect against Bad Randomness.
%\emph{Advances in Cryptology~-- ASIACRYPT `09}, 
%  LNCS vol. 5912, pp. 232--249. Springer, 2009

\item \label{FLJLPR14}
\authorfont{M. Fredrikson, E. Lantz, S. Jha, S. Lin, D. Page, and T.
Ristenpart}.
Privacy in Pharmacogenetics: An End-to-End Case Study of Personalized Warfarin Dosing.
\emph{USENIX Security Symposium}, USENIX, 2014

%\end{revnumerate}
\myenumend


%\bibliographypub{cv-pub}
%\input{pub.bbl}


%\newpage 
%\begin{center}\highlight{\Large{Thomas C. Ristenpart}}\end{center}\bigskip

%\nociteman{R05}
%\bibliographystyleman{mine}
%\newcounter{manpointnumber}
%\setcounter{manpointnumber}{2} % nummans + 1
%\makeatletter
%\renewcommand*{\@biblabel}[1]{[\themanpointnumber
%\addtocounter{manpointnumber}{-1}]}
%\makeatother
%\bibliographyman{cv-man}
%\input{man.bbl}
\bigskip



%%%%%
\noindent\secfont{Synergistic Activities}

\myitemize
\item \highlight{Research community service}: 
Fast Software Encryption 2009, 2010 / Selected Areas in Cryptography 2010 /
Cloud Computing Security Workshop 2010, 2011 (co-Program chair), 2012, 2013,
2014  /
Financial Crypto 2011 /  HotCloud 2011, 2012 / CCS 2011, 2012 / Eurocrypt 2012,
2014 / 
Oakland 2012, 2013, 2015 / NDSS 2013 / Crypto 2013 / DSN 2014; USENIX Security
2014, 2015 / FOCI 2014 / SoCC 2014 / 
Journal of Cryptology / Designs, Codes and Cryptography / Journal of Computer Security. 
Organizing committee for a new workshop on ``Real World Cryptography'' to promote
the applied crypto research community. General chair Crypto 2015.

%\item \highlight{Invited panels}: NIST ``How to choose SHA-3?''~panel 2008 /
%DARPA ISAT Future Ideas Symposium 2010 / Payment Card Industry 2

\item \highlight{Industry standards}: Techniques from \mycite{DRS09} used 
in evaluating NIST SHA-3 competitors / \mycite{BRRS09} basis for 
NIST and ANSI standard proposal named FFX / \mycite{RTSS09} referenced by
Cloud Security Alliance's cloud security guide, European Network and Information 
Security Agency's report on cloud security / New security issues and analyses
of HMAC (Crypto 2012), TLS (Asiacrypt 2011), and PKCS\#2 (Crypto 2012)
%
\item \highlight{Open-source software}: Adeona privacy-preserving device tracking software
%covered by
%\emph{The New York Times}, \emph{Technology Review}, \emph{ABC News}, and many others.  
downloaded $>$113,000 times since July~2008. Various vulnerabilities found in my work
responsibly disclosed to Mozilla, Google, Microsoft, Intuit, Amazon, and many
other companies. FTE implementations from~\myciteee{DCRS13}{LDJRS14}{LSRJ14} 
open source and public. FTE now deployed with Tor and other anti-censorship
tools.


\item \highlight{Curriculum development}: I developed two new graduate-level 
courses, Applied Cryptography and Computer Security (CS 838), at Wisconsin, and have taught it
successfuly twice.  I developed an entirely new curriculum for the 
existing undergraduate class, Computer Security (CS 642), at Wisconsin.
%The curriculum included significant project components working with virtual machines and
%included some initial content related to cloud computing. 
These classes have been well-received by students, whose evaluations ranked it
repeatedly rank it amongst the very best in the department.

\item \highlight{Student advising including underrepresented groups}: 
Advised or co-advised five graduated 
masters students at Wisconsin  (WesLee Frisby, MS 2012, now at Sandia National Laboratories /  
Thawan Kooburat, MS 2012, first employment at Facebook 
Benjamin Farley, MS 2012, first employment at Amazon, Robert Jellinek, MS 2014, 
first employment Amazon, Alexis Fisher, MS 2013, first employment at Sandia National Laboratories).
Advised two undergraduate student now graduated (Benjamin Moench, BS 2014 and Adam Vail, BS 2012, now at 
Univ of Wisconsin for MS). Currently advising 
one masters student (Lichao Zao), two PhD students (Rahul Chatterjee, Liang
Wang), and co-advising three PhD students (Venkatanathan Varadarajan, Adam Everspaugh, Yan
Zhai).

%%
%\item Mozilla, Google developers acknowledge security vulnerabilities 
%found in \mycite{RY10}
%
%\item Cloud computing attacks~\mycite{RTSS09} featured 
%in \emph{Technology Review}, \emph{PC World}, and others. 
%European Network and Information Security Agency cites my 
%work~\mycite{RTSS09} in report on best practices for
%cloud computing security.
%
%\item Proposed standard for encryption methods for
%credit cards, SSNs, healthcare records based on \mycite{BRRS09}
\myitemizeend

\bigskip


%%%%%
\noindent\secfont{Collaborators \& Other Affiliations}

\myitemize
\item \highlight{Collaborators and Co-Editors}:
Aditya Akella (Univ of Wisconsin),
Mihir Bellare (UC San Diego),
Juan Caballero (IMDEA, Spain),
Stephen Checkoway (Johns Hopkins),
Scott Coull (RedJack),
Drew Davidson (Univ of Wisconsin),
Yevgeniy Dodis (New York Univ),
Kevin Dyer (Portland State Univ),
Adam Everspaugh (Univ of Wisconsin),
Benjamin Farley (Univ of Wisconsin),
Alexis Fisher (Univ of Wisconsin),
Matthew Fredrikson (Univ of Wisconsin),
WesLee Frisby (Univ of Wisconsin),
Aaron Gembler (Univ of Wisconsin),
Matt Green (Johns Hopkins),
Keqiang He (Univ of Wisconsin),
Daniel J. Bernstein (UI Chicago / TU Eindhoven),
Robert Jellinek (Univ of Wisconsin),
Somesh Jha (Univ of Wisconsin),
Ari Juels (Cornell Tech),
Sriram Keelveedhi  (UC San Diego),
Thawan Kooburat (Univ of Wisconsin),
Tanja Lange (TU Eindhoven),
Eric Lantz (Univ of Wisconsin),
Simon Lin (Marshfield Clinic),
Daniel Luchaup (Carnegie Mellon Univ),
Jake Maskiewicz (UC San Diego),
Benjamin Moench (Univ of Wisconsin),
Antonio Nappa (IMDEA, Spain),
Ruben Niederhagen (TU Eindhoven),
David Page (Univ of Wisconsin),
Benjamin Recht (Berkeley),
Michael Reiter (Univ North Carolina),
Hovav Shacham (UC San Diego),
Thomas Shrimpton (Portland State Univ),
John Steinberger (Tsinghua Univ, China),
Michael Swift (Univ of Wisconsin),
Stefano Tessaro (UC Santa Barbara),
Salil Vadhan (Harvard),
Venkatanathan Varadarajan  (Univ of Wisconsin),
Liang Wang (Univ of Wisconsin),
Scott Yilek (St. Thomas Univ),
Yan Zhai (Univ of Wisconsin),
Yinqian Zhang (Univ North Carolina)
\item \highlight{Graduate Advisors and Postdoctoral Sponsors}: Mihir Bellare (UC San Diego)
\item \highlight{Thesis Advisor and Postgraduate-Scholar Sponsor}: Matt Bishop (UC Davis)
\myitemizeend



\end{document}

